\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-13 3-advanced.Rmd
section 4.2

One task that may interest analysts in spatio-temporal data is to find how similar time series, from nearby sites, are. This problem can be seen as a matching problem [@stuart2010matching; @mcintosh2018using] that pairs up similar time series in nearby locations or a data fusing exercise that merges data collected from different sources [@cocchi2019data]. \code{match_sites()} in \pkg{cubble} provides a simple algorithm for this task. The algorithm first matches the two data sources spatially by computing the pairwise distance on latitude and longitude. After that, pairs that pass the spatial matching are then matched temporally by computing the number of matched peaks within a fixed length moving window. Figure \ref{fig:illu-matching} illustrates this temporal matching in more detail. Given two series \code{A} and \code{a}, three peaks have been identified in each series. An interval, with default length of five, is constructed for each peak in series \code{A}, while the peaks in series \code{a} are tested against whether they fall into any of the intervals. In this illustration, there are two matches for these two series. Several arguments are available in \code{match_sites()} to fine-tune the matching:

>>>>

One task that may interest spatio-temporal analysts is matching data collected at nearby but not exactly the same sites, for example, weather station measured rainfall and river levels. This can be considered to be a matching problem [@stuart2010matching; @mcintosh2018using] to pair similar time series from nearby locations, or even a data fusion exercise that merges data collected from different sources [@cocchi2019data]. The function \code{match_sites()} in \pkg{cubble} provides a simple algorithm for this task. The algorithm first matches spatially by computing the pairwise distance on latitude and longitude. Then it matches temporally by computing the number of matched peaks within a fixed length moving window. Figure \ref{fig:illu-matching} illustrates this temporal matching. In the two series, \code{A} and \code{a}, three peaks have been identified in each. An interval, of fixed length, is constructed for each peak in series \code{A}, while the peaks in series \code{a} are tested against whether they fall into any of the intervals. Here two out of three peaks match. Options for \code{match_sites()} are:

### 2022-06-13 jss/cubble-jss.tex
section 4.2

One task that may interest analysts in spatio-temporal data is to find how similar time series, from nearby sites, are. This problem can be seen as a matching problem \citep{stuart2010matching, mcintosh2018using} that pairs up similar time series in nearby locations or a data fusing exercise that merges data collected from different sources \citep{cocchi2019data}. \code{match_sites()} in \pkg{cubble} provides a simple algorithm for this task. The algorithm first matches the two data sources spatially by computing the pairwise distance on latitude and longitude. After that, pairs that pass the spatial matching are then matched temporally by computing the number of matched peaks within a fixed length moving window. Figure \ref{fig:illu-matching} illustrates this temporal matching in more detail. Given two series \code{A} and \code{a}, three peaks have been identified in each series. An interval, with default length of five, is constructed for each peak in series \code{A}, while the peaks in series \code{a} are tested against whether they fall into any of the intervals. In this illustration, there are two matches for these two series. Several arguments are available in \code{match_sites()} to fine-tune the matching:

>>>>

One task that may interest spatio-temporal analysts is matching data collected at nearby but not exactly the same sites, for example, weather station measured rainfall and river levels. This can be considered to be a matching problem \citep{stuart2010matching, mcintosh2018using} to pair similar time series from nearby locations, or even a data fusion exercise that merges data collected from different sources \citep{cocchi2019data}. The function \code{match_sites()} in \pkg{cubble} provides a simple algorithm for this task. The algorithm first matches spatially by computing the pairwise distance on latitude and longitude. Then it matches temporally by computing the number of matched peaks within a fixed length moving window. Figure \ref{fig:illu-matching} illustrates this temporal matching. In the two series, \code{A} and \code{a}, three peaks have been identified in each. An interval, of fixed length, is constructed for each peak in series \code{A}, while the peaks in series \code{a} are tested against whether they fall into any of the intervals. Here two out of three peaks match. Options for \code{match_sites()} are:
